---
title: "Homework III"
author: "Javier Galván Fraile - Jorge Medina Hernández"
date: "4/03/2020"
output: 
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, error=FALSE, message=FALSE}
#Libraries used:
library(rsubgroup)
```

# Introduction 

In this task we will use the [crime database]( https://data.lacity.org/A-Safe-City/Crime-Data-from-2010-to-2019/63jg-8b9z) from the Police Department of Los Angeles, which describes the features of each crime committed in LA between 2010 and 2019, although we will only analyze the ones which took place along 2019. 

The main goal is to discover subgroups among data and analyze their quality, interest and interpretation.

```{r, include=FALSE}
##We will skip most of the data and then select only those of 2019
#DB <- read.csv(file='Crime_Data_from_2010_to_2019.csv',skip=17e5)
#headings <- read.csv('Crime_Data_from_2010_to_2019.csv',nrows=1)
##The DB does not have the propper headings:
#names(DB)<- names(headings)
```

We will directly load the data from 2019 alone and show an example to see its structure:
```{r}
DB <- read.csv(file='Crime_Data_2019.csv')
head(DB,n=1L)
```



# Subgroups

# Quality measurement

# Discussion